---
title: "p8105 hw5 solutions"
author: "Shuhong Xiang"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document

---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 12, 
  fig.height = 8,
	fig.path='Figs/',
  out.width = "90%",
	options(digit = 3)
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

## Problem 1

### Load the data.

```{r}
homcide_df =
  read_csv("homcide_data/homicide-data.csv") %>%
  mutate(
    city_state = str_c(city, state, sep = "_"), 
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>%
  select(city_state, resolved) %>%
  filter(city_state != "Tulsa_AL")

```

```{r}
aggregate_df = 
  homcide_df %>%
  group_by(city_state) %>%
  summarise(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

### Prop test for a single city: 

```{r}
prop.test(
  aggregate_df%>%filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df%>%filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>%
  broom::tidy()
```

### Try to iterate:

```{r}
results_df = 
  aggregate_df %>%
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>%
  select(-prop_tests) %>%
  unnest(tidy_tests) %>%
  select(city_state, estimate, conf.low, conf.high)
```

```{r}
results_df %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate))+
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

### Create path_df containing all data from the csv:

```{r}
path_df =
  tibble(
  path = list.files("lda_data"),
) %>%
  mutate(path = str_c("lda_data/", path),
         data = map(path, read_csv)
           )%>%
  unnest(data)

path_df
```

### Clean the datafram:

```{r}
tidy_lda =
  path_df %>%
  mutate(
    path = str_remove_all(path,"lda_data/"), 
    path = str_remove_all(path,".csv")
  ) %>%
  separate(path, into = c("group","subject_id"), sep = 3) %>%
  mutate(
    subject_id = str_remove_all(subject_id, "_"),
    group = str_replace(group,"con","control"),
    group = str_replace(group,"exp","experiment")
  )%>%
  pivot_longer(
    week_1:week_8,
    names_prefix = "week_",
    names_to = "week",
    values_to = "weekly observations"
  )%>%
  mutate(week = as.numeric(week))
tidy_lda
```

### Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups:

```{r}
plot_p2 =
  tidy_lda %>%
  unite("id", c(group, subject_id), sep = "_", remove = F) %>%
  ggplot(aes(x = week,
             y = `weekly observations`)) +
  geom_point(aes(color = group,
                group = id),
             alpha = .5)+
  geom_path(aes(color = group,
                group = as.factor(id)),
            alpha = 0.5) +
  geom_smooth(aes(color = group), method = loess, se = F)

ggsave("plot_p2.png", path = "Figs")

plot_p2
```

From the graph above, we can see that the control groups and experiment groups began the study at the same level of weekly observations. As the study goes on, the control group remain steadily around the same level as beginning  whereas the experiment groups increase gradually. 

## Problem 3

Conduct a simulation to explore power in a one-sample t-test.

### First set n =30 and sigma =5 for the whole problem. Then, set μ=0. Generate 5000 datasets from the model $$x ~ Normal[mu, sigma]$$ :

```{r}
mu_0 <- 0
n_sim <- 5000

set.seed(5000)

 t_test_mu_0 = function(n = 30, mu, sigma = 5) {
  
  t_test_df = tibble(
    
    x = rnorm(n =30, mean = mu, sd = sigma)
  )
  
  t_test_df %>%
    summarise(
      mu_estimated = mean(x),
      p_val = t.test(x, conf.level = 0.95) %>% broom::tidy() %>% pull(p.value)
    )
}

results_mu_0 = vector("list", n_sim)

for(i in 1 : n_sim){
  
  results_mu_0[[i]] = t_test_mu_0(mu = mu_0)
  
}

sim_mu_0 = bind_rows(results_mu_0)
sim_mu_0
```

### Repeat the above for μ={1,2,3,4,5,6}:

```{r}
set.seed(5000)

sim_t_test = function(n = 30, mu, sigma = 5) {
  
  results_6_mu = vector("list", n_sim)
  
  for(i in 1:n_sim){
    
    results_6_mu[[i]] = t_test_mu_0(mu = mu)
    
  }
  results_sim_t_test = bind_rows(results_6_mu)
}

sim_6_mu = vector("list", 6)

for(i in 1:6){
  
  sim_6_mu[[i]] = sim_t_test(mu = i)
  
}

  results_all = bind_rows(sim_6_mu)

  results_all
```

